Fetch PMC Citation Info

### 2021-04-29 citation_fetching.Rmd
script works

---
title: "Fetch Citation Info"
author: "Mark Ziemann"
date: "28/04/2021"
output: html_document
---

@@

@@

>>>>

---
title: "Fetch PMC Citation Info"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    fig_width: 7
    fig_height: 7
theme: cosmo
---

@@

library("reutils")

@@

## Try the following

Now to get a bunch of these.

```{r,reutils3}

PMCIDS <- c("PMC6317205", "PMC6317219", "PMC6318854", "PMC6318897", "PMC6322516", "PMC6323737", "PMC6323741", "PMC6325784", "PMC6325795", "PMC6325889", "PMC6326702", "PMC6327033",
            "PMC6327913", "PMC6328174", "PMC6328465", "PMC6328499", "PMC6329100", "PMC6329100", "PMC6329125", "PMC6329125", "PMC6329193", "PMC6329348")

PMCIDS <- as.numeric(gsub("PMC","",PMCIDS))

res <- sapply(X = PMCIDS, FUN = get_cites)

res
```

Looks like it works :)

## Session information

```{r,sessioninfo}

sessionInfo()
